On change of priors in one-vs-one classification methods

### 2025-05-20 paper.tex
Revised introduction; added graph to Experiment 1

Multi-class classification is considered to be a more challenging problem than binary classification.  A natural approach to multi-class classification is to reduce it to a series of binary classification problems and deduce the multi-class decision by aggregating decisions for the binary problems.

One popular method belonging to  this paradigm uses probabilistic modelling for one-vs-one series of binary problems. Notably, it is used as the basis for multi-class classification models using support vector machines (SVM) in LIBSVM library. However one can use the approach more generally,  because it can be applied to any probabilistic binary classification method.

>>>>

Distribution shift is an important problem facing machine-learning practitioners. The shift is almost inevitable since most real-worlds environments evolve over time. One particular way a distribution shift may manifest in classification problems  is when the class priors change. To make a concrete example, imagine a driver assistance system recognizing traffic signs. The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city. This of course affects classification, and a good classification system will be able to improve its performance when supplied with a new set of more accurate class priors.

Change of priors can be effectively dealt with in probabilistic classifiers. The basic idea is that Bayes theorem stipulates \emph{exactly} what should happen  to the prediction of the  Bayes classifier.  In practice we assume that a trained classifier closely approximates the Bayes classifier. Therefore we can make adjustment to our prediction by applying the same transformation of posterior as would happen with the Bayes classifier.

There is a subtle issue with this approach  when handling probabilistic classifiers arising in one-vs-one classification framework.   One-vs-one classification is a natural framework to approach  multi-class classification by reducing it to a series of binary classification problems. One then deduces the multi-class decision by aggregating decisions for the binary problems. Since the procedure is two-step, there is possibility to apply adjustment of priors either during the first step, or the second step, and it is not clear what should be the preferred course of action.

One-vs-one classification is commonly by machine learning practitioners when they opt to use support vector classifiers or support vector machines. Why is that users opt one-vs-one classification when there are multi-class extensions of SVM such as the proposed by Crammer-Singer?  One possible reason is that there is no \emph{canonical} extension. A second reason is that the multi-class optimization problems have to deal with multiple
